---
title: "CashCosts"
author: "rod-"
date: "June 24, 2015"
output: html_document
---

An analysis of gem spending in WD.
Assume your goal is to get powerful dragons, because come on that's the point of the game, right?

Speeding up egg missions:
```{r}
#baseline for fresh: 
#1h=30 4h=92
basictime<-c(3600)
basiccost<-c(30)
midcost<-c(92,65)
midtime<-c(14400,9240)
expcost<-c(7,6,457)
exptime<-c(600,480,72000)
#4h is worth 80 while 1h is worth 20 and 20h is worth 160.

```
The cost to speed up these missions appears to be semi-linear and varies across mission type in a way that makes it more expensive to speed up higher missions:  
Therefore, the 20-token 1hour missions are probably the most bang/buck (assuming you don't mind actually doing them).  
You get 40 tokens for 30 gems.  

The direct purchase of egg tokens is 34/200gems , so don't do that!

Darja costs 17950 gems, which could be ~24000 tokens.  Given that generally there is a .15 chance of getting a 'new' fragment through the orange range, and that chance is currently reduced to .1 by 
the devs, it costs 133 tokens for a new fragment.  You could earn 180 new fragments for the cost of a darja, pushing you forward by 3 or 4 dragons, well into other epics and legendaries..

```{r, echo=FALSE}
plot(everything)
```

